Fuzzy joins through deep learning

### 2018-07-27 paper2018/siamese_networks.tex
more cleaned up version of loss functions

\subsection{Loss functions}
\label{loss_functions}
Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
\subsubsection{Triplet loss}
For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$.  For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
\begin{equation}
  l_{triple} =  \left[\|\bf{x_a} - \bf{x_p}\|^2 - \|\bf{x_a} -\bf{x_n}\|^2 + \alpha \right]_+
\label{schroff}
\end{equation}
where
\begin{equation}
 \left[.\right]_{+} = max(0, .)
\end{equation}
and the loss function that is minimized across all $N$ triples is given by
\begin{equation}
 L = \sum_{i}^{N} l_{triple}
\end{equation}
Note that in this formulation, it is assumed that embedding is normalized so $\|\bf{x} \| = 1$ because this normalization is robust across variations in illumination and contrast.  The value of $\alpha$ in the original work is a hyper-parameter that \cite{DBLP:conf/cvpr/SchroffKP15} was set to 0.2.

\subsubsection{Improved Loss}
 An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.  In addition, they try to correct that  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.

\begin{equation}
  \psi = \sum_{i}^N(\left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - \hat{\alpha} \right]
\label{psi}
\end{equation}
\begin{equation}
  \phi = \|f(x_i^a) - f(x_i^p)\|_{2}^2 - \left( (\|f(x_i^a)- f(x_i^n)\|_{2}^2 + \|f(x_i^p) - f(x_i^n)\|_{2}^2) / 2 \right) + \alpha
\label{phi}
\end{equation}
\begin{equation}
  L = max(0, \phi) + \lambda * max(0, \psi)
\label{improved_loss}
\end{equation}
The parameter $\hat{\alpha}$ for equation~\ref{psi} is set to 0.1, and $\lambda$ is set to .02 in equation~\ref{improved_loss}, and $\alpha$ was set to 1 in the paper \cite{Zhang:2016:DML:3088616.3088665}.

\subsubsection{Angular Loss}
Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.  Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.  Their loss function is an attempt to minimize this angle, as defined in the equation below.

\begin{equation}
L = max(0, \left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - 4 \tan^2 \alpha \|f(x_i^n) - f(x_i^c)\|_{2}^2 \right])
\end{equation}

>>>>

\subsection{Loss functions}
\label{loss_functions}
Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
\subsubsection{Triplet loss}

\begin{figure}
\includegraphics[width=1.0\linewidth]{schroff_triplet}
\caption{Triplet loss}
\label{schroff_loss}
\end{figure}

For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$, as shown in Figure~\ref{schroff_loss}.  For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
\begin{equation}
  l_{triple} =  \left[\|\bf{x_a} - \bf{x_p}\|^2 - \|\bf{x_a} -\bf{x_n}\|^2 + \alpha \right]_+
\label{schroff}
\end{equation}
where
\begin{equation}
 \left[.\right]_{+} = max(0, .)
\end{equation}
and the loss function that is minimized across all $N$ triples is given by
\begin{equation}
 L = \sum_{i}^{N} l_{triple}
\end{equation}
Note that in this formulation, it is assumed that embedding is normalized so $\|\bf{x} \| = 1$ because this normalization is robust across variations in illumination and contrast.  The value of $\alpha$ in the original work is a hyper-parameter that \cite{DBLP:conf/cvpr/SchroffKP15} was set to 0.2.

\subsubsection{Improved Loss}
 An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.  In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.

\begin{equation}
  \psi_{triple} = \|\bf{x_{a}} - \bf{x_{p}}\|^2 - \hat{\alpha}
\label{psi}
\end{equation}
\begin{equation}
  \phi_{triple} = \|\bf{x_{a}} - \bf{x_{p}}\|^2 - (\|\bf{x_{a}}- \bf{x_{n}}\|^2 + \|\bf{x_{p}} - \bf{x_{n}}\|^2) / 2  + \alpha
\label{phi}
\end{equation}
\begin{equation}
  l_{triple} = max(0, \phi) + \lambda * max(0, \psi)
\label{improved_loss}
\end{equation}
The parameter $\hat{\alpha}$ for equation~\ref{psi} is set to 0.1, and $\lambda$ is set to .02 in equation~\ref{improved_loss}, and $\alpha$ was set to 1 in the paper \cite{Zhang:2016:DML:3088616.3088665}.  As in Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15}, the embeddings are normalized to 1.

\subsubsection{Angular Loss}
Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.  Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.  Their loss function is an attempt to minimize this angle, as defined in the equation below.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}
